The \dealii Library, Version 9.5

### 2023-06-15 9.5/paper.tex
Add a couple of numbers.

While there are no new \dealii tutorial programs in this release, many
were extensively revised.
\todo[inline]{See if we can say something more concrete.}

>>>>

While there are no new \dealii tutorial programs in this release, many
were extensively revised: Around 130 of the more than 2000 (non-merge)
commits that went into this release touched the tutorial, in some
cases adding substantial amounts of text.

% data generated using these commands:
% - tutorial: git log --since 2022/06/01 --no-merges examples | grep commit | wc -l
% - total:    git log --since 2022/06/01 --no-merges | grep commit | wc -l
